The ANthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2024-02-15 paper.tex
MLH changes 2024-02-15 _2

This means, among other things, that all relevant anatomical entities (bones, teeth, their parts and composite structures) must each be located in one subtree (i.e., must have a common superclass) rather than spread across the entire ontology.

>>>>

This means, among other things, that all relevant anatomical entities (bones, teeth, their parts and composite structures) must each be located in one subtree (i.e., must have a common superclass) rather than spread across the entire ontology, as is the case with FMA.
